Coupling

### 2019-12-08 coupling.tex
coupling roughly done

Here, we collect all terms involving only $A, \phi, \psi$:
\begin{align*}
& 
\end{align*}

@@

Here, we collect all terms involving only $A, \phi$ and $\psi$:

@@

Here, we collect all terms depending only on $\lambda^*, \phi$ and $c$:
\[
- (\lambda^*, \mu([c, \phi], \phi) Q) + (\lambda^*, [c, Q \mu(\phi,\phi)]) .
\]
Since $\mu : U^{\otimes 2} \to \fg^*$ is $\fg$-invariant, this expression vanishes. 
\end{proof}

@@

Next, we expand $\{I_{\rm couple}, I^{(2)}_{\rm matter}\}$:
\begin{align*}
\{I_{\rm couple}, I^{(2)}_{\rm matter}\} = & (\rho(\Gamma(Q_1,Q_2)) \psi^*, [A, \psi]) + (\lambda, \mu(\phi, \rho(\Gamma(Q_1,Q_2)) \psi^*)) +  (\psi^*, [c, \rho(\Gamma(Q_1,Q_2)) \psi^*])
\end{align*}

Expanding $\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\}$:
\begin{align*}
\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\} = (\phi^* Q_1 , \rho([A,\phi]) Q_2) + \brian{finish}
\end{align*}

>>>>

First, we collect all terms involving only $A, \phi$ and $\psi$.
This is obtained by extracting the $A$-dependent terms in the expression
\[
\pm (\d_A(Q, \psi), \d_A \psi) \pm (\rho(\d_A\phi)Q, \sd \dd_A \psi) .
\]
The proof that this expression vanishes is identical to the proof of Lemma \ref{lem: hyper1}.

@@

@@

Here, we collect all terms depending only on $\lambda^*, \phi$ and $c$:
\[
- (\lambda^*, \mu([c, \phi], \phi) Q) + (\lambda^*, [c, Q \mu(\phi,\phi)]) .
\]
Since the moment map $\mu$ is $\fg$-invariant, this expression vanishes. 
\end{proof}

@@

Next, we expand $\{I_{\rm couple}, I^{(2)}_{\rm matter}\}$:
\begin{align*}
\{I_{\rm couple}, I^{(2)}_{\rm matter}\} (Q_1,Q_2) = & (\rho(\Gamma(Q_1,Q_2)) \psi^*, [A, \psi]) + (\lambda, \mu(\phi, \rho(\Gamma(Q_1,Q_2)) \psi^*)) \\ & + (\Gamma(Q_1, Q_2), \Gamma([c, \psi^*], \psi^*)) + (\Gamma(Q_1, Q_2), \Gamma(\psi^*, [c, \psi^*])).
\end{align*} 
The last line vanishes by the $\fg$-invariance of the symplectic pairing for $U$.

Expanding $\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\}$:
\begin{align*}
\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\}(Q_1,Q_2) = & (\psi^*, \rho([\Gamma(Q_1, \lambda), \phi]) Q_2) + (\psi^*, \rho([\Gamma(Q_2, \lambda), \phi]) Q_1) \\ + & (A^*, \Gamma(Q_1, \mu(\phi, \phi) Q_2)) - (A^*, \Gamma(Q_2, \mu(\phi, \phi) Q_1)) . 
\end{align*}
Notice the term proportional to $A^*$ vanishes.

\begin{align*}
\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\}  (Q_1,Q_2) = & (\phi^* Q_1 , \rho([A,\phi]) Q_2) + (\phi^* Q_2 , \rho([A,\phi]) Q_1) \\ + &  (\psi^*, \rho([A, (Q_1, \psi)]) Q_2) +  (\psi^*, \rho([A, (Q_2, \psi)]) Q_1) \\ + & (\lambda^*, \mu((Q_1, \psi), \phi) Q_2) +  (\lambda^*, \mu((Q_2, \psi), \phi) Q_1) 
\end{align*}

We collect terms involving $\phi, A$ and $\phi^*$:
\[
\pm [i_{\Gamma(Q_1, Q_2)} A, \phi] + (Q_1, \rho([A,\phi])Q_2) + (Q_2, \rho([A,\phi])Q_1)
\]
By Proposition \ref{prop:cliffordactionproperties} the last two terms cancel with the first term.

Next, we collect terms involving $\phi, \psi$ and $\lambda^*$. 
This term is obtained by taking the $\fg$-pairing of $\mu(\phi, \psi)$ with
\[
\pm \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*) Q_2
\]
which vanishes by Proposition \ref{prop: new3psi}.

Next, we collect terms involving $\lambda, \phi, \psi^*$.
This term can be written as pairing the antifield $\psi^*$ with the field
\[
\rho(\Gamma(Q_1,Q_2)) [\lambda, \phi] + \rho([\Gamma(Q_1,\lambda), \phi]) Q_2  + \rho([\Gamma(Q_2,\lambda), \phi]) Q_1. 
\]
This whole expression is equal to applying the $\fg$-valued field 
\[
\rho(\Gamma(Q_1,Q_2)) \lambda + \rho(\Gamma(Q_1,\lambda)) Q_2  + \rho(\Gamma(Q_2,\lambda)) Q_1
\]
to the field $\phi$ by the representation. 
This expression vanished by Proposition \ref{prop:3psi}.

Finally, we collect terms involving $\psi^*,A$ and $\psi$.
This can be written as the pairing of the antifield $\psi^*$ with the field
\[
\pm [A, \rho(\Gamma(Q_1,Q_2)) \psi] + \rho([A, (Q_1, \psi)]) Q_2 + \rho([A, (Q_2, \psi)]) Q_1 .
\] 
This expression is equal to applying the $\fg$-valued field $A$ to the field
\[
\pm \rho(\Gamma(Q_1,Q_2)) \psi + (Q_1, \psi) Q_2 + (Q_2, \psi) Q_1
\]
which vanishes by Proposition \ref{prop: new3psi}.
